\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-07-29 minimal.tex
versioning 1.2.6

>>>>

\attachment[click me][view][local]{examples/attachment/pdf\_reference.pdf} to view pdf\_reference.pdf embedded from local storage. \\
\attachment[click me][download][local]{examples/attachment/pdf\_reference.pdf} to download pdf\_reference.pdf embedded from local storage. \\
\attachment[click me][view][local]{examples/attachment/big\_mountain.png} to view big\_mountain.png embedded from local storage. \\
\attachment[click me][view][web]{https://www.google.de/} to view Google.html embedded from web storage. \\
\attachment[click me][download][local]{examples/attachment/Google.html} to download Google.html embedded from local storage. \\
\attachment[click me][view][web]{http://www.khazanah.com.my/khazanah/files/20/200f21f3-07ff-4903-ab99-7c0cb557eb51.pdf} to view pdf\_reference.pdf embedded from web storage. \\
\attachment[click me][download][web]{http://www.khazanah.com.my/khazanah/files/20/200f21f3-07ff-4903-ab99-7c0cb557eb51.pdf} to download pdf\_reference.pdf embedded from web storage. \\

\graph[width=0.75\textwidth, height=0.5\textwidth]{examples/graphs/graph.txt} \\
